\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}
\usepackage{hyperref}

% Reduce vertical spacing globally
\setlength{\parskip}{0pt}
\setlength{\itemsep}{0pt}
\setlength{\parsep}{0pt}
\setlength{\topsep}{0pt}

\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

% Preamble
\firstname{Pavel}
\familyname{Machalek PhD}
\address{San Francisco, California, United States}{}

\begin{document}
\makecvtitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C C}
    \emailsymbol\enspace \emaillink{pavel@machalek.io} & \faLinkedin\enspace \href{https://www.linkedin.com/in/pavel-machalek-0152b8269}{linkedin.com/in/pavel-machalek-0152b8269}
&
    \mobilephonesymbol\enspace (415) 890-6659 &
    \faGithub\enspace \href{https://github.com/ivanmladek}{github.com/ivanmladek}

\end{tabularx}
\vspace{-2.0mm}

% LEFT COLUMN
\begin{minipage}[t]{0.62\textwidth}
\section{EXPERIENCE}

\experienceentry{SpaceKnow Inc.}{AI Pretraining Infrastructure Lead}{2023--Present}{San Francisco}
\begin{itemize}
    \item Designed, built, and maintained a distributed data pipeline for LLM pretraining, ingesting and processing terabytes of multimodal data (text and images).
    \item Engineered and optimized data storage and processing infrastructure for petabyte-scale datasets, ensuring efficient data delivery for model training.
    \item Collaborated with research teams to refine data recipes through rigorous experimentation, leading to significant improvements in model performance.
    \item Fine-tuned and deployed a variety of open-source LLMs, including Llama-2, Mistral, and Phi-3, for a variety of downstream tasks.
\end{itemize}


\experienceentry{Spartacus Inc.}{Chief Technology Officer}{2018--2023}{San Francisco, CA}
\begin{itemize}
    \item Built privacy risk scoring engine using advanced machine learning approaches with Python, analyzing 250+ data points per user across 100+ data brokers, achieving 92\% accuracy.
    \item Designed and deployed intelligent data protection systems using TensorFlow and PyTorch for real-time threat detection and mitigation.
    \item Pioneered implementation of AutoGPT and BabyAGI frameworks (post-2023) for autonomous task execution in privacy protection workflows.
\end{itemize}

\experienceentry{SpaceKnow Inc.}{Co-Founder, Board Member, CEO }{2013--2018}{San Francisco Bay Area}
\begin{itemize}
    \item Led the development of SpaceKnow Satellite Activity Index using advanced machine learning, processing over 2 million square kilometers daily using Docker and TensorFlow.
    \item Architected geospatial analytics platform integrating computer vision systems for strategic influence on AI product direction.

\end{itemize}

\experienceentry{The Climate Corporation}{Senior Data Scientist}{2011--2013}{San Francisco Bay Area}
\begin{itemize}
    \item Reduced corn yield prediction error from ±15.2\% to ±12.1\% across 6.2M acres through advanced machine learning implementations.
    \item Built ETL pipelines processing 14TB/day of MODIS/Landsat data on 256-node distributed computing cluster.
\end{itemize}

\experienceentry{NASA Ames Research Center}{Senior Scientist}{2009--2011}{Mountain View, CA}
\begin{itemize}
    \item Improved Kepler photometry precision to 29ppm (from 42ppm) using innovative signal processing algorithms.
    \item Processed 1.7M star light curves using CUDA-accelerated pipelines with custom optimization techniques.
\end{itemize}

\end{minipage}
\hfill
% RIGHT COLUMN
\begin{minipage}[t]{0.35\textwidth}
\section{SUMMARY}
Research engineer with deep experience in pretraining infrastructure, distributed data pipelines, and high-throughput scraping systems. PhD in Astrophysics from Johns Hopkins. Built and scaled ML infra for LLMs, scientific, and geospatial domains. Focused on robust, reproducible, and scalable data and ML systems.

\section{CORE SKILLS}
\textbf{Data \& ML Infrastructure} \\
Distributed ETL, data lakes, cloud pipelines (AWS/GCP), Kubernetes, Spark, Airflow, Dask, batch/stream processing, S3, Parquet, BigQuery, MLflow, 

\textbf{Scraping \& Web Data} \\
Playwright, RedisBloom for deduplication, scalable proxy rotation, 1,000+ QPS scraping, robust error handling, BullMQ, high-volume web data acquisition

\textbf{ML \& Preprocessing} \\
OCR (Nougat), NLTK, langdetect, feature extraction, tokenization, PyTorch, TensorFlow, ONNX, GGML, JAX, automated benchmarking, MLOps

\section{EDUCATION}
\educationentry{PhD in Astrophysics}{The Johns Hopkins University}{2004--2009}{Baltimore, MD}
\\

PATENT \textbf{US10839211B2} \\
Multi-resolution multi-spectral deep learning based change detection for satellite images \\
\emph{Inventors: Michal Reinstein, Jakub Simanek, Pavel Machalek, Jan Zikes} \\
Assignee: SpaceKnow Inc. \\
Filed: Aug 2017, Granted: Nov 2020 \\

\end{minipage}

\end{document}
